---
title: "About"
author: "Taylor Greenberg Goldy"
date: "2/26/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rsconnect)
library(shiny)
library(janitor)
library(tidyverse)
library(ggplot2)

storesearch <- read.csv("raw_data/storefront_searches_2020-02-29_2020-03-07.csv") %>%
    clean_names()
    
visits <- read.csv("raw_data/visits_2019-01-01_2019-12-31.csv") %>%
    clean_names()


```


This is the link for my repo:
https://github.com/taylorgreenberggoldy/final_project.git

The data I am using for this project is looking at the behavior of customers and interactions they have on a shopping website that I have access to.  In this data, I'll be able to see how often people are shopping, what are they shopping for as well as what are they searching on the website for.  Through this study, I can hopefully be able to make suggestions to how to improve the overal UX of the site to let people navigate it more thoroughly.  I am slowly getting access to more of the data and will be able to add more files into this project however for now, these two provide sufficient data to get started.

To pull this data, I'm looking at shopify as well as google analytics that pulls basic measurements off of the website of the e-commerce site.

```{r first plot}

# For this plot, I wanted to see for each of the months, what was the turnover
# rate and see how many people visited the site, put something in their cart,
# and actually followed through with the process.  To do that, I had to filter
# down my data to only look at the first of each month.  Then I needed to
# reformat my data to tidy to visualize.

purchases <- visits %>%
    filter(day == "2019-01-01"| day == "2019-02-01" | day == "2019-03-01" |  day == "2019-04-01" |  day == 
               "2019-05-01" | day == "2019-06-01" | day == "2019-07-01" | day == "2019-08-01" |  
               day == "2019-09-01" |  day == "2019-10-01" |  day == "2019-11-01" |  day == "2019-12-01") %>%
    pivot_longer(cols = c(total_sessions, total_carts, total_checkouts, total_orders_placed, total_conversion), names_to = "action") 
    
# Then I could plot the results here with month on the x axis and the number of
# actions on the y axis.  I was having trouble renaming the dates to just the
# month name and would love some help on that! I also need some help in
# reordering my bars

ggplot(purchases, aes(x = day, y = value, fill = action))+
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Shopping Turnover for Online Shop",
       y= "Actions", x = "Month")+
    theme(axis.text.x=element_text(angle=45, hjust=1))

```


```{r shiny}
library(shiny)

ui <- navbarPage(
    "Final Project Title",
    tabPanel("Model",
             fluidPage(
                 titlePanel("Model Title"),
                 sidebarLayout(
                     sidebarPanel(
                         selectInput(
                             "plot_type",
                             "Plot Type",
                             c("Option A" = "a", "Option B" = "b")
                         )),
                     mainPanel(plotOutput("line_plot")))
             )),
    tabPanel("Discussion",
             titlePanel("Discussion Title"),
             p("Tour of the modeling choices you made and 
              an explanation of why you made them")),
    tabPanel("About", 
             titlePanel("About"),
             h3("Project Background and Motivations"),
             p("Hello, this is where I talk about my project."),
             h3("About Me"),
             p("My name is Taylor Greenberg Goldy and I study Design Engineering in the Graduate School of Design and School of Engineering and Applied Sciences. This is the link for my repo:
https://github.com/taylorgreenberggoldy/final_project.git

The data I am using for this project is all of the interactions that students do on our syllabus and Preceptors textbook.  One datasource will be DavidKane.info for the syllabus as well as the textbook website that is found on David Kane's github.  From this, we will hopefully be able to analyze how long people are spending on the sites, what are they looking at mostly, and when are peak times of use?

             You can reach me at taylorgg@mde.harvard.edu")))

server <- function(input, output) {
    output$line_plot <- renderPlot({
        # generate type based on input$plot_type from ui
        ifelse(
            input$plot_type == "a",
            # if input$plot_type is "a", plot histogram of "waiting" column 
            # from the faithful dataframe
            x   <- faithful[, 2],
            # if input$plot_type is "b", plot histogram of "eruptions" column
            # from the faithful dataframe
            x   <- faithful[, 1]
        )
        # draw the histogram with the specified number of bins
        hist(x, col = 'darkgray', border = 'white')
    })
}

shinyApp(ui = ui, server = server)
```

